What factors and how influence Zillow Housing Sale Price

### 2024-04-17 paper/paper.qmd
Add files via upload

---
title: "What factors and how influence Zillow Housing Sale Price"
author: 
  - "Yaning Jin"
thanks: "Code and data are available at: https://github.com/Yuki010305/Final-Paper."
date: today
date-format: long
abstract: "This project is interested in the factors affecting housing prices on zillow. After exploratory analysis of the data, a multiple linear regression was constructed, and a log transformation was performed to build a model with better performance. The transformed housing factors can explain more than 80% of the changes in housing prices. However, the existence of residuals in the model does not fully meet the constraints of the normality assumption, so in the future, data processing, feature engineering and model improvement are needed to study the factors affecting Zillow's housing prices.."
format: pdf
number-sections: true
bibliography: references.bib
link-citations: true
---

@@

library(tidyverse)
library(MASS)
library(magrittr)
library(gridExtra)
library(ggplot2)
library(car)
library(stargazer)
library(modelsummary)

@@

One of a nation's key industries is housing, and the health of this sector influences the degree of economic growth of the nation. A person's home is frequently the most expensive item in their life. Zillow is an online real estate database provider that assesses property values and offers details on the houses you're interested in [@loukissas2018all]. The Zestimate prediction system was developed by Zillow. It is based on a data collection of hundreds of millions of homes and provides a preliminary estimate of a property's worth by combining a particular algorithm with the features of each home and the state of the market[@rolli2020zillow]. To improve the accuracy of the Zestimate system and provide people with a more trustworthy way to estimate home prices, Zillow launched the Zillow Awards competition in 2017. Our goal in this project is not to participate in a competition to minimize the logarithmic error between the estimated house price and the actual selling price. The main purpose of our exploration in this project is to explore the factors that affect Zillow home sales prices and how they affect home sales prices. Characteristics of the homes we select include number of bathrooms, number of bedrooms, square footage, number of rooms, year, tax value, land tax value, etc.

@@

@@

@@

@@

```{r}
#| label: summary
#| fig-cap: summary numeric
#| echo: false
summary(zillowtrim[,-c(1,2,4,5)])
```

```{r,echo=FALSE,eval=FALSE}
#| label: air
#| fig-cap: central air table
#| echo: false
### Categorical table
table(zillowtrim$bathroomcnt)
```

@@

par(mfrow=c(1,2))

hist(zillowtrim$bathroomcnt, breaks=10,main="", xlab="bathroom")
hist(zillowtrim$bedroomcnt, breaks=10, main="",xlab="bedroom")

par(mfrow=c(1,2))
boxplot(zillowtrim$calculatedfinishedsquarefeet,xlab="square feet")
boxplot(zillowtrim$roomcnt, xlab="room")

par(mfrow=c(1,2))
boxplot(zillowtrim$taxvaluedollarcnt, xlab="tax value")
boxplot(zillowtrim$landtaxvaluedollarcnt, xlab="land tax value")
```

```{r,warning=FALSE,message=FALSE}
#| label: point
#| fig-cap: points
#| echo: false
a=ggplot(data=zillowtrim, aes(x=bathroomcnt, y=price)) + 
  geom_point() + 
  geom_smooth(method = lm, se = FALSE,size=1.5,color="red") + 
  labs(x = 'bathroom', y='Sale Price')+
  theme_bw()

@@

b=ggplot(data=zillowtrim, aes(x=bedroomcnt, y=price)) + 
  geom_point() + 
  geom_smooth(method = lm, se = FALSE,size=1.5) + 
  labs(x = 'bedroom', y='Sale Price')+
  theme_bw()

@@

```{r}
#| label: full
#| fig-cap: full model
#| echo: false
#| 
### full model
full = lm(log(price) ~ ., data = train)
summary(full)
```

```{r}
#| label: sub
#| fig-cap: sub model
#| echo: false
#| 
log_ml = lm(log(price) ~ bathroomcnt+bedroomcnt+log(calculatedfinishedsquarefeet)+roomcnt+yearbuilt+log(taxvaluedollarcnt)+log(landtaxvaluedollarcnt), data = train)
summary(log_ml)
```

@@

```{r}
#| label: plot1
#| fig-cap: plot model
#| echo: false
#par(mfrow=c(2,2))

#plot(log_ml)
```

@@

```{r}
#| label: model2
#| fig-cap: create model 2
#| echo: false
#| 
ml_new = lm(log(price) ~ bathroomcnt+bedroomcnt+log(calculatedfinishedsquarefeet)+roomcnt+yearbuilt+log(taxvaluedollarcnt)+log(landtaxvaluedollarcnt), data = new_train)
summary(ml_new)
```

@@

```{r}
#| label: plotmodel2
#| fig-cap: plot model 2
#| echo: false
plot(ml_new)
```

@@

>>>>

---
title: "What factors and how influence Zillow Housing Sale Price"
author: 
  - "Yaning Jin"
thanks: "Code and data are available at: https://github.com/Yuki010305/What-factors-and-how-influence-Zillow-Housing-Sale-Price.git."
date: today
date-format: long
abstract: "This project is interested in the factors affecting housing prices on zillow. After exploratory analysis of the data, a multiple linear regression was constructed, and a log transformation was performed to build a model with better performance. The transformed housing factors can explain more than 80% of the changes in housing prices. However, the existence of residuals in the model does not fully meet the constraints of the normality assumption, so in the future, data processing, feature engineering and model improvement are needed to study the factors affecting Zillow's housing prices.."
format: pdf
number-sections: true
bibliography: references.bib
link-citations: true
---

@@

library(tidyverse)
library(gridExtra)
library(ggplot2)
library(stargazer)
library(xtable)
library(modelsummary)
library(kableExtra)
library(tinytex)

@@

One of a nation's key industries is housing, and the health of this sector influences the degree of economic growth of the nation. A person's home is frequently the most expensive item in their life. Zillow is an online real estate database provider that assesses property values and offers details on the houses you're interested in [@loukissas2018all]. The Zestimate prediction system was developed by Zillow. It is based on a data collection of hundreds of millions of homes and provides a preliminary estimate of a property's worth by combining a particular algorithm with the features of each home and the state of the market[@rolli2020zillow]. To improve the accuracy of the Zestimate system and provide people with a more trustworthy way to estimate home prices, Zillow launched the Zillow Awards competition in 2017. Our goal in this project is not to participate in a competition to minimize the logarithmic error between the estimated house price and the actual selling price. The main purpose of our exploration in this project is to explore the factors that affect Zillow home sales prices and how they affect home sales prices. Characteristics of the homes we select include number of bathrooms, number of bedrooms, square footage, number of rooms, year, tax value, land tax value, etc. The estimated model is

$$\text{log(price)}=\beta_0+\beta_1\text{bathrooms}+\beta_2\text{log(squarefootage)}+...+\beta_6\text{taxValue}$$
For some variables we will also do some log transformations.

@@

## Raw Data

In this research, we examine zillow data sourced using the zillbowR library [@rolli2020zillow]. The dataset encompasses 90,275 records (89,499 records after cleaning), focusing on specific variables: bathroom number, bedroom number, year built, square feet, room number, tax value, etc. The apartments were built in a wide range of years, from as early as 1885 to as recently as 2015.

@@

## Data Analysis tools

R [@citeR], a potent open-source statistical programming language, was used to analyze the data. To improve the effectiveness of our data operations, we used a collection of R packages from the tidyverse [@citetidyverse], which is a collection of tools created for data science. The `dplyr` package [@rDplyr] offered a consistent collection of verbs that aid in filtering, summarizing, and organizing the dataset, while the `ggplot2` package [@rGgplot2] made it easier to create complex visualizations. Because of its quick and user-friendly data reading capabilities, the `readr` package [@rReadr] was used.  `Knitr` [@rKnitr] handled report production dynamically, allowing R code to be included into this document. `kableExtra`[@R-kableExtra] was also used to create visually appealing and editable tables, which improved the way our results were presented.

@@

## Variable Description {#sec-variable}

@@

# Exploratory Data Analysis {#sec-exploration}

```{r}
#| label: summary
#| fig-cap: summary numeric
#| echo: false
#summary(zillowtrim[,-c(1,2,4,5)])

#kableExtra::kable(t(zillowtrim[,-c(1,2,4,5)]), format="latex")
```

```{r,echo=FALSE,eval=FALSE}
#| label: air
#| fig-cap: central air table
#| echo: false
### Categorical table
table(zillowtrim$yearbuilt)
```

@@

#par(mfrow=c(1,2))

#hist(zillowtrim$calculatedfinishedsquarefeet, breaks=10,main="", xlab="square feet")
#boxplot(zillowtrim$taxvaluedollarcnt, xlab="tax value")
#hist(zillowtrim$bedroomcnt, breaks=10, main="",xlab="bedroom")

#par(mfrow=c(1,2))
#boxplot(zillowtrim$calculatedfinishedsquarefeet,xlab="square feet")
#boxplot(zillowtrim$roomcnt, xlab="room")

#par(mfrow=c(1,2))
#boxplot(zillowtrim$taxvaluedollarcnt, xlab="tax value")
#boxplot(zillowtrim$landtaxvaluedollarcnt, xlab="land tax value")
```

```{r,warning=FALSE,message=FALSE}
#| label: point
#| fig-cap: points
#| echo: false
#a=ggplot(data=zillowtrim, aes(x=bathroomcnt, y=price)) + 
#  geom_point() + 
#  geom_smooth(method = lm, se = FALSE,size=1.5,color="red") + 
#  labs(x = 'bathroom', y='Sale Price')+
#  theme_bw()

#b=ggplot(data=zillowtrim, aes(x=taxvaluedollarcnt, y=price)) + 
#  geom_point() + 
#  geom_smooth(method = lm, se = FALSE,size=1.5) + 
#  labs(x = 'tax value', y='Sale Price')+
#  theme_bw()

#grid.arrange(a,b, nrow=1)
```

@@

@@

```{r}
#| label: full
#| fig-cap: full model
#| echo: false
#| 
### full model
full = lm(log(price) ~ ., data = train)
#summary(full)
```

```{r}
#| label: sub
#| fig-cap: sub model
#| echo: false
#| 
log_ml = lm(log(price) ~ bathroomcnt+bedroomcnt+log(calculatedfinishedsquarefeet)+roomcnt+yearbuilt+log(taxvaluedollarcnt)+log(landtaxvaluedollarcnt), data = train)
#summary(log_ml)
```

@@

```{r}
#| label: plot1
#| fig-cap: plot model
#| echo: false
#par(mfrow=c(2,2))
#plot(log_ml)
```

@@

```{r}
#| label: model2
#| fig-cap: create model 2
#| echo: false
#| 
ml_new = lm(log(price) ~ bathroomcnt+bedroomcnt+log(calculatedfinishedsquarefeet)+roomcnt+yearbuilt+log(taxvaluedollarcnt)+log(landtaxvaluedollarcnt), data = new_train)
summary(ml_new)
#latex_code <- stargazer(full, log_ml, ml_new,type = "latex", title = "Regression Results" ,align = TRUE)
#cat(latex_code, file = "regression_results.tex")
#xelatex("regression_results.tex")
```

@@

```{r}
#| label: plotmodel2
#| fig-cap: plot model 2
#| echo: false
#plot(ml_new)
```

@@

```{r}
#| label: plotresidual
#| fig-cap: plot resid
#| echo: false
#| 
plot(ml_new, which=1)
